Results

### 2019-06-24 analysis/03_analysis.Rmd

# Load data
# results <- readRDS(here("data", "derived_data", "results.rds"))
```

@@

>>>>

# Specify the model to load
intercept <- 1 # Intercept-only

# Load and extract data and model output (see model-calibration.R)
if (intercept == 1) {
  run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.RDS"))
  data <- run$data
  fit <- run$fit
}
```

@@

# Model checking

```{r model-checking}
source(here::here("R", "stan_utility.R"))

# Check for divergences
check_div(fit)

# # Check the effective sample size (not working for a hierarchical model?)
# check_n_eff(fit)
# 
# # Check the Rhat statistic (not working for a hierarchical model?)
# check_rhat(fit)

# Check trace plots
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    regex_pars = "Theta",
    n_warmup = 1000,
    facet_args = list(nrow = 2, labeller = label_parsed)
  )

# colnames(fit$Gammadraw) <- str_c("Gamma[", c(1:ncol(fit$Gammadraw)), ",1]")
# fit$Gammadraw %>%
#   mcmc_trace(
#     n_warmup = 500,
#     facet_args = list(nrow = 5, labeller = label_parsed)
#   )

ggsave(
  "intercept_trace_noncentered.png",
  path = here::here("analysis", "output", "figures"),
  width = 12, height = 6, units = "in"
)
```

# Extract draws

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

# colnames(fit$Gammadraw) <- str_c("Gamma[", c(1:ncol(fit$Gammadraw)), ",1]")
# draws <- as_tibble(fit$Gammadraw) %>%
#   mutate(
#     .draw = row_number(),
#     .iteration = row_number()
#   ) %>%
#   gather(key = i, value = Gamma, -c(.draw, .iteration)) %>%
#   separate(col = i, into = c("temp1", "i"), sep = "\\[") %>%
#   separate(col = i, into = c("i", "j"), sep = ",") %>%
#   separate(col = j, into = c("j", "temp2"), sep = "\\]") %>%
#   mutate(
#     .chain = as.integer(1),
#     i = as.integer(i),
#     j = as.integer(j)
#   ) %>%
#   select(.chain, .iteration, .draw, i, j, Gamma) %>%
#   arrange(.iteration) %>%
#   filter(.iteration > 500)

# Save draws
write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
```

# Plot marginals

```{r plot-marginals}
# Plot marginals
level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
  "Financial transparency: Yes",
  "Accountability: Yes",
  str_c("Funding sources: ", c("Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")),
  str_c("Relationship with host government: ", c("Criticized by government", "Under government crackdown"))
)
draws %>% 
  mutate(
    levels = factor(
      i,
      labels = level_labels
    )
  ) %>%
  ggplot(aes(x = Theta, y = levels)) + 
  geom_halfeyeh(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Attribute Levels")

# Save plot
ggsave(
  "intercept_marginal-posteriors_noncentered.png",
  path = here::here("analysis", "output", "figures"),
  width = 12, height = 6, units = "in"
)
```
